% arara: pdflatex: { synctex: yes }
% arara: makeindex: { style: ctuthesis }
% arara: bibtex

% The class takes all the key=value arguments that \ctusetup does,
% and a couple more: draft and oneside
\documentclass[twoside]{ctuthesis}

\ctusetup{
	preprint = \ctuverlog,
%	mainlanguage = english,
%	titlelanguage = czech,
	mainlanguage = czech,
	otherlanguages = {english},
	title-czech = {Zásuvný modul QGIS pro~výpočet~erozního~smyvu~na~orné půdě},
	title-english = {Soil Loss on Arable Land QGIS Plugin},
	subtitle-czech = {},
	subtitle-english = {},
	doctype = B,
	faculty = F1,
	department-czech = {Katedra geomatiky},
	department-english = {Department of Geomatics},
	author = {Radek Novotný},
	supervisor = {Ing. Martin Landa, Ph.D.},
	supervisor-address = {ČVUT v Praze - Fakulta stavební, \\ Thákurova 2077/7, Praha 6\\ B802},
	%supervisor-specialist = {John Doe},
	fieldofstudy-english = {Mathematical Engineering},
	subfieldofstudy-english = {Mathematical Modelling},
	fieldofstudy-czech = {Geodézie, kartografie a geoinformatika},
	subfieldofstudy-czech = {Geodézie a kartografie},
	keywords-czech = {slovo, klíč},
	keywords-english = {word, key},
	day = 28,
	month = 5,
	year = 2017,
	specification-file = {ctutest-zadani.pdf},
%	front-specification = true,
%	front-list-of-figures = false,
%	front-list-of-tables = false,
%	monochrome = true,
%	layout-short = true,
}

\ctuprocess

\addto\ctucaptionsczech{%
	\def\supervisorname{Vedoucí}%
	\def\subfieldofstudyname{Studijní program}%
}

\ctutemplateset{maketitle twocolumn default}{
	\begin{twocolumnfrontmatterpage}
		\ctutemplate{twocolumn.thanks}
		\ctutemplate{twocolumn.declaration}
		\ctutemplate{twocolumn.abstract.in.titlelanguage}
		\ctutemplate{twocolumn.abstract.in.secondlanguage}
		\ctutemplate{twocolumn.tableofcontents}
		\ctutemplate{twocolumn.listoffigures}
	\end{twocolumnfrontmatterpage}
}

% Theorem declarations, this is the reasonable default, anybody can do what they wish.
% If you prefer theorems in italics rather than slanted, use \theoremstyle{plainit}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{note}
\newtheorem*{remark*}{Remark}
\newtheorem{remark}[theorem]{Remark}

\setlength{\parskip}{5ex plus 0.2ex minus 0.2ex}

% Abstract in Czech
\begin{abstract-czech}
Cílem bakalářské práce je návrh softwarového nástroje pro výpočet a prezentaci erozního smyvu na orné půdě, který je podkladem pro agrotechnická a organizační opatření při projektování komplexních pozemkových úprav, případně opatření proti nežádoucím vlivům odtokových poměrů. Výstupem aplikace je rastrový soubor prezentující hodnotu erozního smyvu v tunách na hektar za rok (t/ha.rok) pomocí barevné škály v zájmovém území a souhrnná tabulka obsahující výsledné hodnoty erozně hodnocených ploch.

Jako platforma pro vývoj nástroje bude použit programovací jazyk Python, grafický framework PyQt, open source desktopový program QGIS a jeho API (rozhraní pro programovaní aplikací). Nástroj bude implementován ve formě tzv. zásuvného modulu pod licencí GNU GPL.
\end{abstract-czech}

% Abstract in English
\begin{abstract-english}
 Let us suppose we are given a modulus $d$.  In \cite{cite:10}, the main result was the extension of Newton random variables.  We show that ${\Gamma_{\mathfrak{{r}},b}} ( {Z_{\beta,f}} ) \sim \bar{E}$.  The work in \cite{cite:20} did not consider the infinite, hyper-reversible, local case. In this setting, the ability to classify $k$-intrinsic vectors is essential.
 
Let us suppose $\mathfrak{{a}} > \mathfrak{{c}}''$.  Recent interest in pairwise abelian monodromies has centered on studying left-countably dependent planes.  We show that $\Delta \ge 0$.  It was Brouwer who first asked whether classes can be described. B. Artin \cite{cite:30} improved upon the results of M. Bernoulli by deriving nonnegative classes.
\end{abstract-english}

% Acknowledgements / Podekovani
\begin{thanks}
Děkuji ČVUT, že mi je tak dobrou \emph{alma mater}.
\end{thanks}

% Declaration / Prohlaseni
\begin{declaration}
Prohlašuji, že jsem předloženou práci vypracoval samostatně, a že jsem uvedl veškerou použitou literaturu.

V Praze, \ctufield{day}.~\monthinlanguage{title}~\ctufield{year}
\end{declaration}

% Only for testing purposes
\listfiles
\usepackage[pagewise]{lineno}
\usepackage{lipsum,blindtext}
\usepackage{mathrsfs} % provides \mathscr used in the ridiculous examples

\begin{document}

\maketitle



\input{1-eroze}


\appendix

\printindex

\appendix


\end{document}